---
title: "Untitled"
author: "Smriti karki"
date: "10/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#loading library
```{r}
library(haven)
library(dplyr)
library(tidyverse)
library(lubridate)
```
#loading dataset
```{r} 
adaeisr <- read_sas("E:/Numeric mind/adam/New_Study-master/New_Study-master/adam/adaeisr.sas7bdat",NULL)
adae <- read_sas("E:/Numeric mind/adam/New_Study-master/New_Study-master/adam/adae.sas7bdat",NULL)
adsl <- read_sas("E:/Numeric mind/adam/New_Study-master/New_Study-master/adam/adsl.sas7bdat",NULL)
```

```{r}
adaeisr1 <- adae %>% select(STUDYID,USUBJID,APHASE,APHASEN,AESTDTC,ASTDT,ASTDTC,ASTDTF,AEENDTC,AENDT,AENDTC,AENDTF,ASTDY,AENDY,AESEQ,AETERM,AEDECOD,AEBODSYS,AEBDSYCD,AELLT,AELLTCD,AEPTCD,AEHLT,AEHLTCD,AEHLGT,AEHLGTCD,AESOC,AESOCCD,ADURN,ADURU,ADURC,AEACN,AEREFID,AESER,AEOUT,AEOUTN,AEREL,AETOXGR,AETOX,AETOXGRN,AFTRTSTC,ALTRTSTC,ATTRTSTC,AEWD,AECAT,AESHOSP,AESDTH,AESMIE,AESLIFE,AESCONG,AESDISAB,AESRECHA,AESPROT,AESAFTRT,AESREL,ALAT,DRUG)
temp <- adsl %>% select(SITEID,USUBJID,LTSUBJID,AGE,AGEU,SEX,RACE,COUNTRY,SCRNFL,SAFFL,ITTEFL,PPROTFL,ENRLFL,LTFUFL,TRT01P,TRT01PN,TRT01A,TRT01AN,TRTSDT,TRTEDT,MNTEDT,WEIGHTBL)

adaeisr1 <- adaeisr1 %>% full_join(temp)
adaeisr1 <- adaeisr1 %>% filter(APHASE== "Maintenance" & AETERM== "STUDY DRUG INJECTION SITE" & AESER== "Y" | AECAT=="INJECTION SITE REACTION")
rm(temp)

```
```{r}
adaeisr1$TRTP <- adaeisr1$TRT01P
adaeisr1$TRTPN <- adaeisr1$TRT01PN
adaeisr1$TRTA <- adaeisr1$TRT01A
adaeisr1$TRTAN <- adaeisr1$TRT01AN
```
 If analysis AE end date is not missing then AENIMDY = analysis AE end date (ADAE.AENDT)  - date of first exposure to treatment (ADSL.TRTSDT) + 1. If analysis AE end date is missing then AENIMDY = date of last study contact -  date of first exposure to treatment (ADSL.TRTSDT) + 1. #AENIMDY(40)
```{r}
# temp <- adaeisr1 %>% mutate(AENIMDY = case_when(
#   is.na(AENDT) ~ ls- TRTSDT + 1,
#   TRUE ~ AENDT -TRTSDT + 1))
```
#ISRCAT(84)
```{r}
adaeisr1 <-  adaeisr1 %>% mutate(ISRCAT = case_when(
  DRUG == "CAB LA" | DRUG == "RPV LA" ~ "CAB LA and/or RPV LA"))
adaeisr1$ISRCAT[is.na(adaeisr1$ISRCAT)]<- ""
```
#ISRCATCD(85)
```{r}
adaeisr1 <- adaeisr1 %>% mutate(ISRCATCD = case_when(
  ISRCAT == "CAB LA and/or RPV LA" ~ "ISRALL",
  TRUE~ ""))
```
#If  1<=ADURN<=7 then '1-7', else if 8<=ADURN<=14 then '8'-14', else if ADURN>14 then '>14', else blank
#AEDURGP(86)
```{r}
adaeisr1 <- adaeisr1 %>% mutate(AEDURGP= case_when(
  ADURN >= 8 & ADURN <= 14 ~ "8-14",
  ADURN >= 14 ~ ">14",
 ADURN >=1 & ADURN <=7 ~ "1-7",
 TRUE ~ ""))
```
#AEDURCD(87)
```{r}
adaeisr1 <- adaeisr1 %>% mutate(AEDURCD = case_when(
  AEDURGP == "1-7" ~ 1,
  AEDURGP == "8-14" ~ 2,
  AEDURGP == ">14" ~ 3))
```
#Maximum ADURN by USUBJID and APHASE
#MAXDUR(88)
```{r}
adaeisr1 <- adaeisr1 %>%
  group_by(USUBJID,APHASE) %>% 
  mutate(MAXDUR= max(ADURN)) %>% 
  ungroup()
```
#CMAXDUR(89)
```{r}
adaeisr1 <- adaeisr1 %>% 
  group_by(USUBJID,AEDECOD,APHASE) %>% 
  mutate(CMAXDUR= max(ADURN)) %>% 
  ungroup()
```
#If 1<=MAXDUR<=7 then '1-7', If 8<=MAXDUR<=14 then '8-14', If 14<MAXDUR then '>14', otherwise blank
#MXSUBDR(90)
```{r}
adaeisr1 <- adaeisr1 %>% 
  mutate(MXSUBDR = case_when(
    MAXDUR >= 1 & MAXDUR <= 7 ~ "1-7",
    MAXDUR >= 8 & MAXDUR <= 14 ~ "8-14",
    MAXDUR >14 ~ ">14",
    TRUE ~ ""))
```
#IF MXSUBDR =  '1-7' THEN 1, IF MXSUBDR =  '8-14' THEN 2, IF MXSUBDR ='>14' THEN 3, OTHERWISE MISSING
#MXSBDRCD(91)
```{r}
adaeisr1 <- adaeisr1 %>% mutate(MXSBDRCD = case_when(
  MXSUBDR == "1-7" ~ 1,
  MXSUBDR == "8-14" ~2,
  MXSUBDR == ">14" ~3))
```

#If 1<=CMAXDUR<=7 then '1-7', If 8<=CMAXDUR<=14 then '8-14', If 14<CMAXDUR then '>14', otherwise blank
#CMXSBDR(92)
```{r}
adaeisr1 <- adaeisr1 %>% 
  mutate(CMXSBDR = case_when(
    CMAXDUR >= 1 & CMAXDUR<= 7 ~ "1-7",
    CMAXDUR >=8 & CMAXDUR<= 14 ~ "8-14",
    CMAXDUR >14 ~ ">14",
    TRUE ~ ""))
```
#IF CMXSBDR =  '1-7' THEN 1, IF CMXSBDR =  '8-14' THEN 2, IF CMXSBDR ='>14' THEN 3, OTHERWISE MISSING
#CMXSDRCD(93)
```{r}
adaeisr1 <- adaeisr1 %>% 
  mutate(CMXSDRCD = case_when(
    CMXSBDR == "1-7" ~1,
    CMXSBDR == "8-14" ~2,
    CMXSBDR == ">14" ~3))
```
#Y' if AETOXGRN in (3 4 5)
#GR35FL(94)
```{r}
adaeisr1 <- adaeisr1 %>%
  mutate(GR35FL = case_when(
  AETOXGR == "3"| AETOXGR =="4" |AETOXGR == "5" ~"Y"))
adaeisr1$GR35FL[is.na(adaeisr1$GR35FL)] <- ""
```
#EVERATE
#NUMEVE


