---
title: "Untitled"
author: "Smriti karki"
date: "9/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##library loading
```{r}
library(haven)
library(dplyr)
library(Hmisc)
library(tidyverse)
library(expss)
```
```{r}
adds <- read_sas("E:/Numeric mind/adam/New_Study-master/New_Study-master/adam/adds.sas7bdat",NULL)
ds <- read_sas("E:/Numeric mind/adam/New_Study-master/New_Study-master/sdtm/ds.sas7bdat",NULL)
adsl <- read_sas("E:/Numeric mind/adam/New_Study-master/New_Study-master/adam/adsl.sas7bdat",NULL) 
 suppds <- read_sas("E:/Numeric mind/adam/New_Study-master/New_Study-master/sdtm/suppds.sas7bdat",NULL)
```
#combine ds and suppds
```{r}
suppds$IDVARVAL <- as.numeric(suppds$IDVARVAL)
suppds <- suppds %>% rename(DSSEQ = IDVARVAL)

ds_supds<- ds %>% full_join(suppds,by = c("USUBJID", "STUDYID" , "DSSEQ"))
```

#filtering required dataset
```{r}
temp <- ds_supds %>%  
  filter(DSCAT == "DISPOSITION EVENT") %>% 
  filter(DSSCAT != c("GENETICS RESEARCH (FURTHER RESEARCH)","GENETICS RESEARCH (PRIMARY RESEARCH)","STUDY (FURTHER RESEARCH)","STUDY (PRIMARY RESEARCH)")) %>% 
  filter(DSDECOD != "COMPLETED") %>% 
  filter(DSSCAT!= "") %>% 
  filter(DSSCAT != "STUDY" & DSCAT != "PROTOCOL MILESTONE" & DSDECOD != "INFORMED CONSENT OBTAINED") %>%
  filter(DSTERM != "WITHDREW ICF PER TX ENROLLMENT ERROR.  GSK REQUEST TO CORRECTLY ENROLLED AS #00029.")
```
##APHASE(29)
```{r}
temp <- temp %>% mutate(APHASE =case_when(
  EPOCH == "SCREENING" ~ str_to_title("SCREENING"),
  EPOCH == "TREATMENT" ~ "Maintenance",
  EPOCH == "FOLLOW-UP" ~ "Long-term Follow-up"))
```
##APHASEN(30)
```{r}
temp <- temp %>% mutate(APHASEN = case_when(
 APHASE == "Screening" ~ 1,
 APHASE == "Maintenance" ~ 2,
 APHASE == "Long-term Follow-up" ~ 3))
```
#predessor of ds
```{r}
adds1 <- temp %>% rename(SRCSEQ=DSSEQ)
adds1 <- adds1 %>% select(STUDYID,USUBJID, VISIT,VISITNUM,DSSTDTC,SRCSEQ,APHASE,APHASEN)

```
#predecessor from adsl
```{r}
temp1 <- adsl %>%
  select(USUBJID,SITEID,LTSUBJID,AGE,AGEU,SEX,RACE,COUNTRY,SCRNFL,SAFFL,ITTEFL,PPROTFL,ENRLFL,LTFUFL,TRT01P,TRT01PN,TRT01A,TRT01AN,TRTSDT,TRTEDT,MNTEDT)
# USUBJID==c("116482.000066","116482.000151","116482.000274","116482.000603")&,)

# ds <- distinct(ds,USUBJID,.keep_all = T)

  
adds1 <- adds1 %>% left_join(temp1,by = "USUBJID")

```
## TRTP(16) #TRTPN(17) #TRTA(18) #TRTAN(19)
```{r}
adds1 <- adds1 %>% mutate(TRTP = TRT01P)
adds1 <- adds1 %>% mutate(TRTPN = TRT01PN)
adds1 <- adds1 %>% mutate(TRTA = TRT01A)
adds1 <- adds1 %>% mutate(TRTAN = TRT01AN)
```


# ADT(30)
```{r}
a <- as.Date(adds1$DSSTDTC)
adds1 <- adds1 %>% mutate(ADT = a)
rm(a)
```

#If ADT>=ADSL.TRTSDT then ADT-ADSL.TRTSDT+1, else ADT-ADSL.TRTSDT.
#ADY (33)
```{r}
adds1 <- adds1 %>% mutate(ADY= case_when(
  ADT >= TRTSDT ~ ADT- TRTSDT +1,
  TRUE ~ ADT - TRTSDT))
```

```{r}
adds1 <- adds1 %>%
  mutate(AVISIT = case_when(
    (APHASE == "Screening" | APHASE == "Maintenance" ) & ADY <= 1 ~ "Baseline",
    TRT01A == "Q2M" & ADY != "" & ADY <= 1 ~ "Screening",
    TRT01A == "Q2M" & ADY >= 2  & ADY <= 84 ~ "Month 2",
    TRT01A == "Q2M" & ADY >= 85 & ADY <= 140 ~ "Month 4",
    TRT01A == "Q2M" & ADY >= 141 & ADY <= 196 ~ "Month 6",
    TRT01A == "Q2M" & ADY >= 197 & ADY <= 252 ~ "Month 8",
    TRT01A == "Q2M" & ADY >= 252 & ADY <= 308 ~ "Month 10",
    TRT01A == "Q2M" & ADY >= 309 & ADY <= 364 ~ "Month 12",
    TRT01A == "Q2M" & ADY >= 365 & ADY <= 420 ~ "Month 14",
    TRT01A == "Q2M" & ADY >= 421 & ADY <= 476 ~ "Month 16",
    TRT01A == "Q2M" & ADY >= 477 & ADY <= 532 ~ "Month 18",
    TRT01A == "Q2M" & ADY >= 533 & ADY <= 588 ~ "Month 20",
    TRT01A == "Q2M" & ADY >= 589 & ADY <= 644 ~ "Month 22",
    TRT01A == "Q2M" & ADY >= 645 & ADY <= 700 ~ "Month 24",
    TRT01A == "Q2M" & ADY >= 701 & ADY <= 820 ~ "Month 26"))
```
```{r}
adds1 <- adds1 %>%
  mutate(AVISITN = case_when(
    AVISIT == "Baseline" ~ 0,
    AVISIT == "Month 2" ~ 20,
    AVISIT == "Month 4" ~ 40,
    AVISIT == "Month 6" ~ 60,
    AVISIT == "Month 8" ~ 80,
    AVISIT == "Month 10" ~ 100,
    AVISIT == "Month 12" ~ 120,
    AVISIT == "Month 14" ~ 140,
    AVISIT == "Month 16" ~ 160,
    AVISIT == "Month 18" ~ 180,
    AVISIT == "Month 20" ~ 200,
    AVISIT == "Month 22" ~ 220,
    AVISIT == "Month 24" ~ 240,
    AVISIT == "Month 26" ~ 260))
# aa <- adds1 %>% mutate(AVISIT= case_when(
#   ADY =1 & DSSCAT == "STUDY TREATMENT DISCONTINUATION" & DSDECOD == "ADVERSE EVENT" & TRT01A =="Q2M" ~ 20))
```

#'PHSTAT'
```{r}
test_phstat <- temp %>% 
  filter(DSSCAT == "PHASE CONCLUSION" & DSDECOD != "COMPLETED")
``` 
#'PHWRES'
```{r}
test_phwres <- temp%>% filter(DSSCAT == "PHASE CONCLUSION")
```
#'PHWSRES'
```{r}
test_phwsres <- temp %>% filter(DSSCAT  == "PHASE CONCLUSION")
```
#SCSTAT
```{r}
test_scstat <- temp %>% 
  filter(DSSCAT == "STUDY CONCLUSION" & DSDECOD != "COMPLETED") %>% 
  mutate(AVALC="WITHDRAWN") %>% rename(SRCDOM = DOMAIN) %>% 
  mutate(PARAM = "STUDY: COMPLETION STATUS" , PARAMCD = "SCSTAT") %>% 
  select(USUBJID,DSSEQ,AVALC,PARAM,PARAMCD,SRCDOM)
```
#SCWRES
```{r}
test_SCWRES <- temp %>% filter(DSSCAT == "STUDY CONCLUSION") %>% 
  mutate(AVALC = DSDECOD, PARAM = "STUDY: WITHDRAWAL REASON" ,PARAMCD = "SCWRES", SRCVAR = "DSDECOD")%>% 
  rename(SRCDOM = DOMAIN) %>% 
  select(USUBJID,DSSEQ,AVALC,PARAM,PARAMCD,SRCDOM,SRCVAR)
  
```
#'SCWSRES'
```{r}
test_SCWSRES <- temp %>% filter(DSSCAT == "STUDY CONCLUSION" & DSDECOD!= DSTERM) %>% 
  mutate(AVALC = DSTERM,PARAM = "STUDY: WITHDRAWAL SUB REASON", PARAMCD = "SCWSRES",SRCVAR = "DSTERM")%>% 
  rename(SRCDOM = DOMAIN) %>% 
  select(USUBJID,DSSEQ,AVALC,PARAM,PARAMCD,SRCDOM,SRCVAR)
```
#'SFRES'
```{r}
test_sfres <- temp %>% filter(DSSCAT == "SCREEN") %>% 
  mutate(AVALC = DSDECOD, PARAM = "SCREENING: REASON FOR FAILURE", PARAMCD = "SFRES",SRCVAR = "DSDECOD")%>% 
  rename(SRCDOM = DOMAIN) %>% 
  select(USUBJID,DSSEQ,AVALC,PARAM,PARAMCD,SRCDOM,SRCVAR)
```
#SFSRES
```{r}
test_sfsres <- temp %>% filter(DSSCAT == "SCREEN" & DSTERM != DSDECOD) %>% 
  mutate(AVALC = DSTERM, PARAM = "SCREENING: SUB REASON FOR FAILURE", PARAMCD = "SFSRES",SRCVAR = "DSTERM")%>% 
  rename(SRCDOM = DOMAIN) %>% 
  select(USUBJID,DSSEQ,AVALC,PARAM,PARAMCD,SRCDOM,SRCVAR)
  
```
#'SFSTAT'
```{r}
test_sfstat <- temp %>% filter(DSSCAT == "SCREEN" & DSDECOD != "COMPLETED") %>% 
  mutate(AVALC = "FAILED", PARAM = "SCREENING: STATUS", PARAMCD = "SFSTAT")%>% 
  rename(SRCDOM = DOMAIN) %>% 
  select(USUBJID,DSSEQ,AVALC,PARAM,PARAMCD,SRCDOM)
```
#TCSTAT 
```{r}
test_tcstat <- temp %>% 
  filter(DSSCAT == "STUDY TREATMENT DISCONTINUATION" & DSDECOD != "COMPLETED") %>% 
  mutate(AVALC = "WITHDRAWN", PARAM = "TREATMENT: COMPLETION STATUS", PARAMCD = "TCSTAT")%>%
  rename(SRCDOM = DOMAIN) %>% 
  select(USUBJID,DSSEQ,AVALC,PARAM,PARAMCD,SRCDOM)

```
#'TCWRES'  
```{r}
test_tcwres <- temp %>% filter(DSSCAT == "STUDY TREATMENT DISCONTINUATION" ) %>% 
  mutate(AVALC = DSDECOD , PARAM = "TREATMENT: WITHDRAWAL REASON", PARAMCD = "TCWRES",SRCVAR = "DSDECOD")%>%
  rename(SRCDOM = DOMAIN) %>% 
  select(USUBJID,DSSEQ,AVALC,PARAM,PARAMCD,SRCDOM,SRCVAR)
```
#'TCWSRES'
```{r}
test_tcwsres <- temp %>% filter(DSSCAT == "STUDY TREATMENT DISCONTINUATION"& DSTERM != DSDECOD) %>% 
  mutate(AVALC = DSTERM, PARAM = "TREATMENT: WITHDRAWAL SUB REASON", PARAMCD = "TCWSRES", SRCVAR = "DSTERM")%>%
  rename(SRCDOM = DOMAIN) %>% 
  select(USUBJID,DSSEQ,AVALC,PARAM,PARAMCD,SRCDOM,SRCVAR)
```

```{r}
AVALC <- bind_rows(list(test_phstat,test_phwres,test_phwsres,test_scstat,test_SCWRES,test_SCWSRES,test_sfres,test_sfsres,test_sfstat,test_tcstat,test_tcwres,test_tcwsres))

avalc <- distinct(.data = AVALC ) %>% select(USUBJID,DSSEQ,AVALC,PARAM,PARAMCD,SRCDOM,SRCVAR)

avalc$SRCVAR[is.na(avalc$SRCVAR)] <- ""
```

#If DS.DSSCAT='SCREEN' then PARCAT1='SCREEN FAILURE', else set to DS.DSSCAT based on VLM attached to AVALC.
```{r}
temp2 <- temp %>% mutate(PARCAT1 = case_when(
  DSSCAT == "SCREEN" ~ "SCREEN FAILURE",
  DSSCAT == "STUDY CONCLUSION" ~ DSSCAT,
  DSDECOD == "CONTINUATION TO FOLLOW UP PHASE" ~ "PHASE CONCLUSION",
  DSSCAT == "STUDY TREATMENT DISCONTINUATION" ~ DSSCAT))
```
```{r}
aaa <- temp2 %>%
  mutate(PARCAT1N = case_when(
  PARCAT1 == "STUDY CONCLUSION" ~ 1,
  PARCAT1 == "SCREEN FAILURE" ~ 2,
  PARCAT1 == "PHASE CONCLUSION" ~ 3,
  PARCAT1 == "STUDY TREATMENT DISCONTINUATION" ~ 4)) %>% 
  select(STUDYID,USUBJID,PARCAT1,PARCAT1N,DSSEQ)

```
```{r}
adds1 <-left_join(adds1,avalc,by = c("USUBJID"="USUBJID","SRCSEQ"="DSSEQ"))
adds1 <- distinct(adds1)
adds1<- left_join(adds1,aaa, by = c("USUBJID"="USUBJID","SRCSEQ"="DSSEQ","STUDYID"="STUDYID"))
adds1 <- distinct(adds1)
```

#SUPPDS.QVAL where SUPPDS.QNAM="FUCERTLM"
```{r}
x<- suppds %>% filter(QNAM == "FUCERTLM") %>% 
  mutate(FUCERTLM = QNAM) %>% 
  select(USUBJID,FUCERTLM)
```
#SUPPDS.QVAL where SUPPDS.QNAM="FUPCONT3"
```{r}
y <- suppds %>% filter(QNAM == "FUPCONT3") %>% 
  mutate(FUPCONT3 = QNAM) %>% 
  select(USUBJID,FUPCONT3)
```
If APHASE = "Maintenance" then: If ((TRT01A = "Q2M" and sDT <= max(LSTORLDT+1, LSTINJDT+67)) or (TRT01A = "DTG + RPV" and sDT <= LSTORLDT+1)) then TRTSTATE = "On-treatment"; else if ((TRT01A = "Q2M" and sDT > max(LSTORLDT+1, LSTINJDT+67)) or (TRT01A = "DTG + RPV" and sDT > LSTORLDT+1)) then TRTSTATE = "Post-treatment".
If APHASE = "Long-Term Follow-Up" then: If sDT <= min(, max(LSTINJDT+67, LSTORLDT+1)) then TRTSTATE = "On-treatment"; else if sDT > min(LTARTSDT, max(LSTINJDT+67, LSTORLDT+1)) then TRTSTATE = "Post-treatment"

#TRTSTATE
```{r}

adds1 <- adds1 %>% mutate(TRTSTATE = case_when(
  APHASE == "Screening"  ~ "Pre-treatment",
  APHASE == "Maintenance"  ~ "On-treatment",
  APHASE == "Long-term Follow-up" ~ "Post-treatment"
))
# temp_adsl <-adsl %>% select(LSTORLDT,LSTINJDT,USUBJID)
# temp_adsl <- left_join(adds1,temp_adsl, by = c("USUBJID"= "USUBJID"))

# temp_adsl <- temp_adsl %>% mutate(TRTSTATE = 
#   ifelse(APHASE == "Screening")  ~ "Pre-treatment",
#   ifelse(APHASE == "Maintenance",
#     ifelse(TRT01A == "Q2M" & ADT <= pmax(LSTORLDT+1, LSTINJDT+67))|(TRT01A == "DTG + RPV" & ADT > pmax(LSTORLDT+1)) ~ "On-treatment"),
#   ifelse(TRT01A == "Q2M" & ADT > pmax(LSTORLDT+1, LSTINJDT+67))|(TRT01A == "DTG + RPV" & ADT > LSTORLDT+1) ~ "Post-treatment",
#   ifelse(APHASE == "Long-term Follow-up",
#     ifelse(TRTSDT> pmin(, pmax(LSTINJDT+67, LSTORLDT+1))~"On-treatment" ,
#   ifelse(TRTSDT> pmin(LTARTSDT, pmax(LSTINJDT+67, LSTORLDT+1))~"Post-treatment"))))
```
```{r}
a <- left_join(x,y,by = c("USUBJID"="USUBJID"))
adds1 <- full_join(adds1,a, by = c("USUBJID" = "USUBJID"))
adds1 <- distinct(adds1,.keep_all = T)
adds1 <- adds1 %>% mutate(DTYPE = " ")

```
```{r}
adds1 <- adds1 %>%  select(STUDYID,SITEID,USUBJID,LTSUBJID,AGE,AGEU,SEX,RACE,COUNTRY,SCRNFL,SAFFL,ITTEFL,PPROTFL,ENRLFL,LTFUFL,TRTP,TRTPN,TRTA,TRTAN,TRT01P,TRT01PN,TRT01A,TRT01AN,TRTSDT,TRTEDT,MNTEDT,VISIT,VISITNUM,APHASE,APHASEN,AVISIT,AVISITN,ADT,ADY,DSSTDTC,PARCAT1,PARCAT1N,PARAM,PARAMCD,AVALC,SRCDOM,SRCVAR,SRCSEQ,FUCERTLM,FUPCONT3,DTYPE,TRTSTATE)
```
```{r}

adds1 <- apply_labels(adds1,TRTP = "Planned Treatment")
adds1 <- apply_labels(adds1,TRTPN = "Planned Treatment (N)")
adds1 <- apply_labels(adds1,TRTA = "Actual Treatment")
adds1 <- apply_labels(adds1,TRTAN = "Actual Treatment (N)")
adds1 <- apply_labels(adds1,APHASE="Phase")
adds1 <- apply_labels(adds1,APHASEN="Phase (N)")
adds1 <- apply_labels(adds1,APHASE="Phase")
adds1 <- apply_labels(adds1,AVISIT="Analysis Visit")
adds1 <- apply_labels(adds1,AVISITN="Analysis Visit (N)")
adds1 <- apply_labels(adds1,ADT="Analysis Date")
adds1 <- apply_labels(adds1,ADY="Analysis Relative Date")
adds1 <- apply_labels(adds1,PARCAT1="Parameter Category 1")
adds1 <- apply_labels(adds1,PARCAT1N="Parameter Category 1 (N)")
adds1 <- apply_labels(adds1,PARAM="Parameter")
adds1 <- apply_labels(adds1,PARAMCD="Parameter Code")
adds1 <- apply_labels(adds1,AVALC="Analysis Value (C)")
adds1 <- apply_labels(adds1,SRCDOM="Source Domain")
adds1 <- apply_labels(adds1,SRCVAR="Source Variable")
adds1 <- apply_labels(adds1,FUCERTLM="Follow-up Certified Letter Mailed")
adds1 <- apply_labels(adds1,FUPCONT3="Follow-up Phone Contact Attempted x3")
adds1 <- apply_labels(adds1,DTYPE="Derivation Type")
adds1 <- apply_labels(adds1,TRTSTATE="Treatment State")
rm(a,aaa,temp,temp1,temp2,test_phstat,test_phwres,test_phwsres,test_scstat,test_SCWRES,test_SCWSRES,test_sfres,test_sfsres,test_sfstat,test_tcstat,test_tcwres,test_tcwsres,x,y,ds_supds,avalc,AVALC)
```



