---
title: "adsl"
author: "Smriti karki"
date: "7/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(haven)
library(readr)
library(readxl)
library(dplyr)
library(tidyverse)

```

## read SDTM raw file (importing files)
```{r}
orig_adsl <- read_sas("C:/Users/Dell/Downloads/New_Study-master/New_Study-master/adam/adsl.sas7bdat",NULL)
dm <- read_sas("C:/Users/Dell/Downloads/New_Study-master/New_Study-master/sdtm/dm.sas7bdat", NULL)
sc <- read_sas("C:/Users/Dell/Downloads/New_Study-master/New_Study-master/sdtm/sc.sas7bdat", NULL)
ds <- read_sas("C:/Users/Dell/Downloads/New_Study-master/New_Study-master/sdtm/ds.sas7bdat", NULL)
suppdm <- read_sas("C:/Users/Dell/Downloads/New_Study-master/New_Study-master/sdtm/suppdm.sas7bdat", NULL)
suppdv <- read_sas("C:/Users/Dell/Downloads/New_Study-master/New_Study-master/sdtm/suppdv.sas7bdat", NULL)
sv <- read_sas("C:/Users/Dell/Downloads/New_Study-master/New_Study-master/sdtm/sv.sas7bdat", NULL)
lb <- read_sas("C:/Users/Dell/Downloads/New_Study-master/New_Study-master/sdtm/lb.sas7bdat", NULL)
ex <- read_sas("C:/Users/Dell/Downloads/New_Study-master/New_Study-master/sdtm/ex.sas7bdat", NULL)
ce <- read_sas("C:/Users/Dell/Downloads/New_Study-master/New_Study-master/sdtm/ce.sas7bdat", NULL)
suppce <- read_sas("C:/Users/Dell/Downloads/New_Study-master/New_Study-master/sdtm/suppce.sas7bdat",NULL)
vs <- read_sas("C:/Users/Dell/Downloads/New_Study-master/New_Study-master/sdtm/vs.sas7bdat",NULL)
mh <- read_sas("C:/Users/Dell/Downloads/New_Study-master/New_Study-master/sdtm/mh.sas7bdat",NULL)
co <- read_sas("C:/Users/Dell/Downloads/New_Study-master/New_Study-master/sdtm/co.sas7bdat",NULL)
c1 <- read_sas("C:/Users/Dell/Downloads/New_Study-master/New_Study-master/sdtm/c1.sas7bdat",NULL)
y8 <- read_sas("C:/Users/Dell/Downloads/New_Study-master/New_Study-master/sdtm/y8.sas7bdat",NULL)
```

# create adsl file
```{r}
adsl_1 <- dm %>% select(STUDYID, INVID, INVNAM, SITEID, USUBJID, AGE, AGEU, BRTHDTC, SEX, RACE, ETHNIC, COUNTRY, ARM, ARMCD, ACTARM, ACTARMCD, DTHFL )
view(adsl_1)
```
##AGEGR1(10)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(AGEGR1 = case_when(
          AGE <35 ~ "<35",
          AGE >= 35 & AGE < 50 ~ "35- <50",
          AGE >= 50 ~ ">= 50"))
```
##AGEGR1N (11)





##AGEGR1N (11)
```{r}
adsl_1 <- adsl_1 %>%
  mutate(AGEGR1N = case_when(
    AGE <35 ~ "1",
    AGE >= 35 & AGE < 50 ~"2",
    AGE >=50 ~ "3"))

```



##AGEGR2(12)
```{r warning=FALSE}
adsl_1 <- adsl_1 %>% 
  mutate(AGEGR2 = case_when(
  AGE <=18 ~"<=18",
  AGE >=19 & AGE <=64 ~"19-64",
  AGE >=65 ~">=65"))
```
##AGEGR2N(13)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(AGEGR2N = case_when(
    AGE <= 18 ~"1",
    AGE >=19 & AGE <=64 ~"2",
    AGE >=65 ~ "3"))
```
##AGEGR3(14)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(AGEGR3 = case_when(
    AGE >=18 & AGE <=64 ~"18-64",
    AGE >=65 & AGE <=84 ~"65-84",
    AGE >=85 ~">=85"))
```
##AGEGR3N(15)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(AGEGR3N =case_when(
    AGE >=18 & AGE <=64 ~"1",
    AGE >=65 & AGE <=84 ~"2",
    AGE >=85 ~"3"))
```
##AGEGR4(16)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(AGEGR4 = case_when(
    AGE < 50 ~"<50",
    AGE >=50 ~">=50"))
```
##AGEGR4N(17)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(AGEGR4N = case_when(
    AGE <50 ~"1",
    AGE >=50 ~"2"))
```
##SEXN(20)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(SEXN = case_when(
    SEX == "F" ~"1",
    SEX == "M" ~"2"))
```
##SRGENDERN(21)
```{r}
sc <-as.data.frame(sc)
gender <- sc %>%select(c(USUBJID,SCTESTCD,SCSTRESC)) %>% 
  filter(SCTESTCD == "GENDER")
adsl_1 <- adsl_1 %>% full_join(gender)
adsl_1 <- distinct(adsl_1, USUBJID , .keep_all = TRUE)

adsl_1 <- adsl_1 %>% 
  mutate(SRGENDER = case_when(
    SCTESTCD=="GENDER"  & SCSTRESC == "FEMALE" ~ "FEMALE",
    SCTESTCD=="GENDER" & SCSTRESC == "MALE" ~ "MALE"))
```
##SRGENDERN(22)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(SRGENDERN = case_when(
    SCTESTCD=="GENDER"  & SCSTRESC == "FEMALE" ~ 1,
    SCTESTCD=="GENDER" & SCSTRESC == "MALE" ~ 2))
```


##RACEN (24)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(RACEN = case_when(
    RACE == "AMERICAN INDIAN OR ALASKA NATIVE  " ~"1",
    RACE == "ASIAN" ~"2",
    RACE == "BLACK OR AFRICAN AMERICAN" ~"3",
    RACE == "MULTIPLE" ~"4",
    RACE == "WHITE" ~"6"))
```
##RACEGR1N(28)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(RACEGR1N = case_when(
    RACE == "WHITE" ~"1",
    RACE != "WHITE" ~"2",
    RACE == "MISSING" ~"3"))
```

##RACEGR2(29)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(RACEGR2 = case_when(
    RACE == "BLACK OR AFRICAN AMERICAN" ~ "BLACK/AFRICAN AMERICAN",
    RACE != "BLACK OR AFRICAN AMERICAN" ~ "NON-BLACK/AFRICAN AMERICAN",
    RACE == "MISSING" ~ "MISSING"))
```
##RACEGR2N(30)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(RACEGR2N = case_when(
    RACE == "BLACK OR AFRICAN AMERICAN" ~"1",
    RACE != "BLACK OR AFRICAN AMERICAN" ~"2",
    RACE == "MISSING" ~ "MISSING"))
```

##ETHNICN(32)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(ETHNICN = case_when(
    ETHNIC == "HISPANIC OR LATINO" ~ "1",
    ETHNIC == "NOT HISPANIC OR LATINO" ~ "2"))
```
##AETHNIC(33)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(AETHNIC = case_when(
    ETHNIC == "NA" ~ "MISSING",
    ETHNIC == "HISPANIC OR LATINO" ~ "HISPANIC OR LATINO",
    ETHNIC == "NOT HISPANIC OR LATINO" ~ "NOT HISPANIC OR LATINO"))
```
##AETHNICN(34)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(AETHNICN = case_when(
    ETHNIC == "NULL" ~ "3",
    ETHNIC == "HISPANIC OR LATINO" ~ "1",
    ETHNIC == "NOT HISPANIC OR LATINO" ~ "2"))
```
##COUNTRYN(36)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(COUNTRYN = case_when(
    COUNTRY == "USA" ~ "13",
    COUNTRY == "CAN" ~ "3"))
```
##TRT01P(57) 
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(TRT01P = case_when(
    ARM == "CAB LA (600 mg) + RPV LA (900 mg) Q2M" ~"Q2M",
    ARM == "Oral DTG (50mg) + RPV (25mg) daily" ~ "DTG+RPV",
    ARM == "Not Assigned" ~"Not Assigned"))
```
##TRT01PN(58)
``` {r}
adsl_1 <- adsl_1 %>% 
  mutate(TRT01PN = case_when(
    ARM == "CAB LA (600 mg) + RPV LA (900 mg) Q2M" ~"1",
    ARM == "Oral DTG (50mg) + RPV (25mg) daily" ~"2",
    ARM == "Not Assigned" ~"999"))
```
##TRT01A(59)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(TRT01A = case_when(
    ACTARM == "CAB LA (600 mg) + RPV LA (900 mg) Q2M" ~ "Q2M",
    ACTARM == "Oral DTG (50mg) + RPV (25mg) daily" ~ "DTG+RPV",
    ACTARM == "Not Assigned" ~"Not Assigned"))
```
##TRT01AN(60)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(TRT01AN = case_when(
    ACTARM == "CAB LA (600 mg) + RPV LA (900 mg) Q2M" ~ "1",
    ACTARM == "Oral DTG (50mg) + RPV (25mg) daily" ~ "2",
    ACTARM == "Not Assigned" ~"999"))
```
##ITTEFL(46)
```{r}
ex <-as.data.frame(ex)
b_1 <- ex %>%  select(c(USUBJID,EXSTDTC))
adsl_1 <- adsl_1 %>% full_join(b_1)

adsl_1 <- adsl_1 %>% 
  mutate(ITTEFL = case_when(
    EXSTDTC == "MIssING" & TRT01P =="MISSING" ~"N",
    EXSTDTC != "MIssING" & TRT01P !="MISSING" ~"Y")) 
  
 
adsl_1 <- distinct(adsl_1,USUBJID,.keep_all = TRUE)
```
##ITTEFLN(45)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(ITTEFLN = case_when(
    EXSTDTC == "MIssING" & TRT01P =="MISSING" ~"0",
    EXSTDTC != "MIssING" & TRT01P !="MISSING" ~"1")) %>% 
  select(-EXSTDTC)
```
##PPROTFL(37)
```{r}
suppdv <- as.data.frame(suppdv)
a_1 <- suppdv %>% select(c(STUDYID,USUBJID))
adsl_1 <- adsl_1 %>% full_join(a_1)

adsl_1 <- adsl_1 %>% 
  mutate(PPROTFL = case_when(
    ITTEFL == "N" ~ "No",
    ITTEFL == "Y" ~ "Yes"))
adsl_1 <- distinct(adsl_1, USUBJID , .keep_all = TRUE)
```
##PPROTFN(38)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(PPROTFN = case_when(
    ITTEFL == "N" ~0,
    ITTEFL == "Y" ~1))
```
##SAFFL(39)
```{r}
ex <- as.data.frame(ex)
b_1 <- ex %>% select(USUBJID,EXSTDTC)
adsl_1 <- adsl_1 %>%  full_join(b_1)
adsl_1 <- distinct(adsl_1,USUBJID,.keep_all = TRUE)
adsl_1 <- adsl_1 %>% 
  mutate(SAFFL = case_when(
    TRT01A != "Not Assigned" & EXSTDTC != "Not Assigned" ~"Y",
    TRUE ~"N"))
```

##SAFFLN(40)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(SAFFLN = case_when(
    TRT01A == "MISSING" & EXSTDTC == "MISSING" ~"0",
    TRT01A != "MISSING" & EXSTDTC != "MISSING" ~"1" )) %>% select(-EXSTDTC)
```
##MNTFL(47)
```{r}
adsl_1 <- adsl_1 %>%
  mutate(MNTFL = case_when(
    ITTEFL == "Y" ~ "Y",
    ITTEFL == "N" ~ "N"))
```
##MNTFLN(48)
```{r}
adsl_1 <- adsl_1 %>%
  mutate(MNTFLN = case_when(
    ITTEFL == "Y" ~ 1,
    ITTEFL == "N" ~ 0))
```
##LTFUEL(49)
```{r}
ds <- as.data.frame(ds)
c_1 <- ds %>% select(c(USUBJID, DSSCAT, EPOCH ,DSDECOD)) 
adsl_1 <- adsl_1 %>% full_join(c_1)

adsl_1 <- adsl_1 %>% 
  mutate(LTFUFL = case_when(
    DSSCAT == "STUDY CONCLUSION" & EPOCH == "FOLLOW-UP" & (DSDECOD == "COMPLETED" | DSDECOD == "CONTINUATION TO FOLLOW UP PHASE")~ "Y" ,
    !(DSSCAT == "STUDY CONCLUSION" & EPOCH == "FOLLOW-UP" & (DSDECOD == "COMPLETED" | DSDECOD == "CONTINUATION TO FOLLOW UP PHASE"))~ "N"))
         
adsl_1 <- distinct(adsl_1,USUBJID,.keep_all = TRUE)
```
##LTFUFLN(50)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(LTFUELN = case_when(
    DSSCAT == "STUDY CONCLUSION" & EPOCH == "FOLLOW-UP" & (DSDECOD == "COMPLETED" | DSDECOD == "CONTINUATION TO FOLLOW UP PHASE")~ 1 ,
    TRUE ~ 0)) %>% select( -EPOCH )
```
##SCRNFL(41)
```{r}
ds <- as.data.frame(ds)
temp41 <- ds %>% select(USUBJID,DSSTDTC,VISITNUM,DSSCAT)
adsl_1 <- adsl_1 %>% full_join(temp41)
adsl_1 <- distinct(adsl_1,USUBJID, .keep_all = TRUE)
sv <- as.data.frame(sv)
temp41.1 <- sv %>% select(USUBJID,SVSTDTC)
adsl_1 <- adsl_1 %>% full_join(temp41.1)
adsl_1 <- distinct(adsl_1,USUBJID,.keep_all = TRUE)
adsl_1 <- adsl_1 %>%
  mutate(SCRNFL = case_when(
    ((toupper(DSSCAT )== "SCREEN" & DSSTDTC != "NULL") | (as.integer(VISITNUM)=="10" & SVSTDTC != "NULL" )) ~"Y",
    TRUE ~ "N"))
```
##SCRNFN(42)
```{r}
adsl_1 <- adsl_1 %>%
  mutate(SCRNFN = case_when(
    (toupper(DSSCAT )== "SCREEN" & DSSTDTC != "NULL") | (as.integer(VISITNUM)=="10" & SVSTDTC != "NULL" ) ~1,
    TRUE ~ 0)) %>% select(-DSSTDTC,-VISITNUM,-SVSTDTC)
```
##ENRLFL(43)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(ENRLFL = case_when(
    DSDECOD == "INFORMED CONSENT OBTAINED" & DSSCAT == "STUDY" ~"N",
    TRUE ~ "Y"))
```
##ENRLFN(44)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(ENRLFN = case_when(
    DSDECOD == "INFORMED CONSENT OBTAINED" & DSSCAT == "STUDY" ~"0",
    TRUE ~ "1"))
```
##CVFFL(51)
```{r}
lb <- as.data.frame(lb)
temp51 <- lb %>% select(USUBJID,LBTESTCD,LBMETHOD,LBSTRESN)
adsl_1 <- adsl_1 %>% full_join(temp51)
adsl_1 <- distinct(adsl_1,USUBJID, .keep_all = TRUE)

adsl_1 <- adsl_1 %>% 
  mutate(CVFFL = case_when(
    LBTESTCD == "HIV1RNA" & LBMETHOD == "POLYMERASE CHAIN REACTION" & LBSTRESN >= "200" ~ "Y",
    TRUE ~ "N"))
```
##CVFFN(52)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(CVFFN = case_when(
    LBTESTCD == "HIV1RNA" & LBMETHOD == "POLYMERASE CHAIN REACTION" & LBSTRESN >= "200" ~ 1,
    TRUE ~ 0)) %>% select(-LBTESTCD,-LBMETHOD,-LBSTRESN)
```
##


##MNTCMPS(63)
```{r}
adsl_1 <- adsl_1 %>% mutate(MNTCMPS = case_when(
  MNTFL == "Y" & DSSCAT == "STUDY CONCLUSION" ~"COMPLETED",
  MNTFL == "Y" & DSSCAT == "STUDY TREATMENT DISCONTINUATION" ~"WITHDRAWN",
  MNTFL == "Y" ~"ONGOING"))
```
##MNTCMPSN(64)
```{r}
adsl_1 <- adsl_1 %>%mutate(MNTCMPSN=case_when(
  MNTCMPS == "ONGOING" ~ 1,
  MNTCMPS == "COMPLETED" ~2,
  MNTCMPS == "WITHDRAWN" ~3))
```
##LTFCMPS(66)not solved...na
ds <-as.data.frame(ds)
d_1 <- ds %>%  select(USUBJID,DSSCAT,EPOCH,DSDECOD) 
adsl_1 <- adsl_1 %>% full_join(d_1)
adsl_1 <- distinct(adsl_1,USUBJID,.keep_all = TRUE)
adsl_1 <- adsl_1 %>% 
  mutate(LTFCMPS=case_when(
    (DSSCAT =="STUDY CONCLUSION" & EPOCH=="FOLLOW-UP" & DSDECOD=="COMPLETED" & TRT01P != "DTG + RPV") ~"COMPLETED",
    (DSDECOD=="CONTINUATION TO FOLLOW UP PHASE" & TRT01P !="DTG + RPV" )~"ONGOING")) %>% 
  select(-DSSCAT,-EPOCH,-DSDECOD)

adsl_1$LTFCMPS[is.na(adsl_1$LTFCMPS)]=""
##LTFCMPSN(67)
adsl_1 <- adsl_1 %>% 
  mutate(LTFCMPSN = case_when(
    LTFCMPS == "ONGOING" ~1,
    LTFCMPS == "COMPLETED" ~2,
    LTFCMPS == "WITHDRAWAL" ~ 3))

##LSEFL(68)
ce <- as.data.frame(ce)
ce_1 <-ce %>% select(c(STUDYID,USUBJID,CECAT))
adsl_1 <- adsl_1 %>% full_join(ce_1)
suppce <- as.data.frame(suppce)
suppce_1 <-suppce %>% select(c(STUDYID, USUBJID,QVAL, QNAM))
adsl_1 <- adsl_1 %>% full_join(suppce_1)
adsl_1 <- distinct(adsl_1,USUBJID,.keep_all = TRUE)  
adsl_1 <- adsl_1 %>% 
  mutate(LSEFL = case_when(
    (CECAT=="LIVER EVENT REPORTING" & suppce$QNAM=="LERMX" & suppce$QVAL=="LIVER EVENT STOPPING CRITERIA") ~"Y",
    !(CECAT=="LIVER EVENT REPORTING" & suppce$QNAM=="LERMX" & suppce$QVAL=="LIVER EVENT STOPPING CRITERIA") ~"N")) %>% 
  select(-CECAT,-QVAL,-QNAM)
##LSEFN(69)
adsl_1 <- adsl_1 %>% 
  mutate(LSEFLN = case_when(
    LSEFL == "Y" ~ 1,
    TRUE ~0))
##DTHFN(71)
adsl_1 <- adsl_1 %>% 
   mutate(DTHFN = case_when(
    DTHFL == "Y" ~ "1",
    TRUE ~ ""))
##ACOUNTRY(72)
adsl_1 <- adsl_1 %>% 
  mutate(ACOUNTRY = case_when(
    COUNTRY == "CAN" ~"CANADA",
    COUNTRY == "USA" ~"UNITED STATES"))
