---
title: "adsl"
author: "Smriti karki"
date: "7/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(haven)
library(readr)
library(readxl)
library(dplyr)
library(tidyverse)

```

## read SDTM raw file (importing files)
```{r}
orig_adsl <- read_sas("E:/Numeric mind/adam/New_Study-master/New_Study-master/adam/adsl.sas7bdat",NULL)
dm <- read_sas("E:/Numeric mind/adam/New_Study-master/New_Study-master/sdtm/dm.sas7bdat",NULL)
sc <- read_sas("E:/Numeric mind/adam/New_Study-master/New_Study-master/sdtm/sc.sas7bdat", NULL)
ds <- read_sas("E:/Numeric mind/adam/New_Study-master/New_Study-master/sdtm/ds.sas7bdat", NULL)
suppdm <- read_sas("E:/Numeric mind/adam/New_Study-master/New_Study-master/sdtm/suppdm.sas7bdat", NULL)
suppdv <- read_sas("E:/Numeric mind/adam/New_Study-master/New_Study-master/sdtm/suppdv.sas7bdat", NULL)
sv <- read_sas("E:/Numeric mind/adam/New_Study-master/New_Study-master/sdtm/sv.sas7bdat", NULL)
lb <- read_sas("E:/Numeric mind/adam/New_Study-master/New_Study-master/sdtm/lb.sas7bdat", NULL)
ex <- read_sas("E:/Numeric mind/adam/New_Study-master/New_Study-master/sdtm/ex.sas7bdat", NULL)
ce <- read_sas("E:/Numeric mind/adam/New_Study-master/New_Study-master/sdtm/ce.sas7bdat", NULL)
suppce <- read_sas("E:/Numeric mind/adam/New_Study-master/New_Study-master/sdtm/suppce.sas7bdat",NULL)
vs <- read_sas("E:/Numeric mind/adam/New_Study-master/New_Study-master/sdtm/vs.sas7bdat",NULL)
mh <- read_sas("E:/Numeric mind/adam/New_Study-master/New_Study-master/sdtm/mh.sas7bdat",NULL)
co <- read_sas("E:/Numeric mind/adam/New_Study-master/New_Study-master/sdtm/co.sas7bdat",NULL)
c1 <- read_sas("E:/Numeric mind/adam/New_Study-master/New_Study-master/sdtm/c1.sas7bdat",NULL)
y8 <- read_sas("E:/Numeric mind/adam/New_Study-master/New_Study-master/sdtm/y8.sas7bdat",NULL)
```

# create adsl file
```{r}
adsl_1 <- dm %>% select(STUDYID, INVID, INVNAM, SITEID, USUBJID, SUBJID, AGE, AGEU, BRTHDTC, SEX, RACE, ETHNIC, COUNTRY, ARM, ARMCD, ACTARM, ACTARMCD, DTHFL )
view(adsl_1)
```
##AGEGR1(10)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(AGEGR1 = case_when(
          AGE <35 ~ "<35",
          AGE >= 35 & AGE < 50 ~ "35- <50",
          AGE >= 50 ~ ">= 50"))
```

##AGEGR1N (11)
```{r}
adsl_1 <- adsl_1 %>%
  mutate(AGEGR1N = case_when(
    AGE <35 ~ "1",
    AGE >= 35 & AGE < 50 ~"2",
    AGE >=50 ~ "3"))

```



##AGEGR2(12)
```{r warning=FALSE}
adsl_1 <- adsl_1 %>% 
  mutate(AGEGR2 = case_when(
  AGE <=18 ~"<=18",
  AGE >=19 & AGE <=64 ~"19-64",
  AGE >=65 ~">=65"))
```
##AGEGR2N(13)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(AGEGR2N = case_when(
    AGE <= 18 ~"1",
    AGE >=19 & AGE <=64 ~"2",
    AGE >=65 ~ "3"))
```
##AGEGR3(14)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(AGEGR3 = case_when(
    AGE >=18 & AGE <=64 ~"18-64",
    AGE >=65 & AGE <=84 ~"65-84",
    AGE >=85 ~">=85"))
```
##AGEGR3N(15)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(AGEGR3N =case_when(
    AGE >=18 & AGE <=64 ~"1",
    AGE >=65 & AGE <=84 ~"2",
    AGE >=85 ~"3"))
```
##AGEGR4(16)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(AGEGR4 = case_when(
    AGE < 50 ~"<50",
    AGE >=50 ~">=50"))
```
##AGEGR4N(17)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(AGEGR4N = case_when(
    AGE <50 ~"1",
    AGE >=50 ~"2"))
```
##SEXN(20)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(SEXN = case_when(
    SEX == "F" ~"1",
    SEX == "M" ~"2"))
```
##SRGENDERN(21)
```{r}
sc <-as.data.frame(sc)
gender <- sc %>%select(c(USUBJID,SCTESTCD,SCSTRESC)) %>% 
  filter(SCTESTCD == "GENDER")
adsl_1 <- adsl_1 %>% full_join(gender)
adsl_1 <- distinct(adsl_1, USUBJID , .keep_all = TRUE)

adsl_1 <- adsl_1 %>% 
  mutate(SRGENDER = case_when(
    SCTESTCD=="GENDER"  & SCSTRESC == "FEMALE" ~ "FEMALE",
    SCTESTCD=="GENDER" & SCSTRESC == "MALE" ~ "MALE"))
```
##SRGENDERN(22)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(SRGENDERN = case_when(
    SCTESTCD=="GENDER"  & SCSTRESC == "FEMALE" ~ 1,
    SCTESTCD=="GENDER" & SCSTRESC == "MALE" ~ 2))
```


##RACEN (24)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(RACEN = case_when(
    RACE == "AMERICAN INDIAN OR ALASKA NATIVE  " ~"1",
    RACE == "ASIAN" ~"2",
    RACE == "BLACK OR AFRICAN AMERICAN" ~"3",
    RACE == "MULTIPLE" ~"4",
    RACE == "WHITE" ~"6"))
```
##RACEGR1N(28)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(RACEGR1N = case_when(
    RACE == "WHITE" ~"1",
    RACE != "WHITE" ~"2",
    RACE == "MISSING" ~"3"))
```

##RACEGR2(29)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(RACEGR2 = case_when(
    RACE == "BLACK OR AFRICAN AMERICAN" ~ "BLACK/AFRICAN AMERICAN",
    RACE != "BLACK OR AFRICAN AMERICAN" ~ "NON-BLACK/AFRICAN AMERICAN",
    RACE == "MISSING" ~ "MISSING"))
```
##RACEGR2N(30)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(RACEGR2N = case_when(
    RACE == "BLACK OR AFRICAN AMERICAN" ~"1",
    RACE != "BLACK OR AFRICAN AMERICAN" ~"2",
    RACE == "MISSING" ~ "MISSING"))
```

##ETHNICN(32)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(ETHNICN = case_when(
    ETHNIC == "HISPANIC OR LATINO" ~ "1",
    ETHNIC == "NOT HISPANIC OR LATINO" ~ "2"))
```
##AETHNIC(33)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(AETHNIC = case_when(
    ETHNIC == "NA" ~ "MISSING",
    ETHNIC == "HISPANIC OR LATINO" ~ "HISPANIC OR LATINO",
    ETHNIC == "NOT HISPANIC OR LATINO" ~ "NOT HISPANIC OR LATINO"))
```
##AETHNICN(34)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(AETHNICN = case_when(
    ETHNIC == "NULL" ~ "3",
    ETHNIC == "HISPANIC OR LATINO" ~ "1",
    ETHNIC == "NOT HISPANIC OR LATINO" ~ "2"))
```
##COUNTRYN(36)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(COUNTRYN = case_when(
    COUNTRY == "USA" ~ "13",
    COUNTRY == "CAN" ~ "3"))
```
##TRT01P(57) 
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(TRT01P = case_when(
    ARM == "CAB LA (600 mg) + RPV LA (900 mg) Q2M" ~"Q2M",
    ARM == "Oral DTG (50mg) + RPV (25mg) daily" ~ "DTG+RPV",
    ARM == "Not Assigned" ~"Not Assigned"))
```
##TRT01PN(58)
``` {r}
adsl_1 <- adsl_1 %>% 
  mutate(TRT01PN = case_when(
    ARM == "CAB LA (600 mg) + RPV LA (900 mg) Q2M" ~"1",
    ARM == "Oral DTG (50mg) + RPV (25mg) daily" ~"2",
    ARM == "Not Assigned" ~"999"))
```
##TRT01A(59)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(TRT01A = case_when(
    ACTARM == "CAB LA (600 mg) + RPV LA (900 mg) Q2M" ~ "Q2M",
    ACTARM == "Oral DTG (50mg) + RPV (25mg) daily" ~ "DTG+RPV",
    ACTARM == "Not Assigned" ~"Not Assigned"))
```
##TRT01AN(60)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(TRT01AN = case_when(
    ACTARM == "CAB LA (600 mg) + RPV LA (900 mg) Q2M" ~ "1",
    ACTARM == "Oral DTG (50mg) + RPV (25mg) daily" ~ "2",
    ACTARM == "Not Assigned" ~"999"))
```
##ITTEFL(46)
```{r}
ex <-as.data.frame(ex)
b_1 <- ex %>%  select(c(USUBJID,EXSTDTC))
adsl_1 <- adsl_1 %>% full_join(b_1)

adsl_1 <- adsl_1 %>% 
  mutate(ITTEFL = case_when(
    EXSTDTC == "MIssING" & TRT01P =="MISSING" ~"N",
    EXSTDTC != "MIssING" & TRT01P !="MISSING" ~"Y")) 
  
 
adsl_1 <- distinct(adsl_1,USUBJID,.keep_all = TRUE)
rm(b_1)
```
##ITTEFLN(45)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(ITTEFLN = case_when(
    EXSTDTC == "MIssING" & TRT01P =="MISSING" ~"0",
    EXSTDTC != "MIssING" & TRT01P !="MISSING" ~"1")) %>% 
  select(-EXSTDTC)
```
##PPROTFL(37)
```{r}
suppdv <- as.data.frame(suppdv)
a_1 <- suppdv %>% select(c(STUDYID,USUBJID))
adsl_1 <- adsl_1 %>% full_join(a_1)

adsl_1 <- adsl_1 %>% 
  mutate(PPROTFL = case_when(
    ITTEFL == "N" ~ "No",
    ITTEFL == "Y" ~ "Yes"))
adsl_1 <- distinct(adsl_1, USUBJID , .keep_all = TRUE)
rm(a_1)
```
##PPROTFN(38)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(PPROTFN = case_when(
    ITTEFL == "N" ~0,
    ITTEFL == "Y" ~1))
```
##SAFFL(39)
```{r}
ex <- as.data.frame(ex)
b_1 <- ex %>% select(USUBJID,EXSTDTC)
adsl_1 <- adsl_1 %>%  full_join(b_1)
adsl_1 <- distinct(adsl_1,USUBJID,.keep_all = TRUE)
adsl_1 <- adsl_1 %>% 
  mutate(SAFFL = case_when(
    TRT01A != "Not Assigned" & EXSTDTC != "Not Assigned" ~"Y",
    TRUE ~"N"))
```

##SAFFN(40)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(SAFFN = case_when(
    TRT01A == "MISSING" & EXSTDTC == "MISSING" ~"0",
    TRT01A != "MISSING" & EXSTDTC != "MISSING" ~"1" )) %>% select(-EXSTDTC)
```
##MNTFL(47)
```{r}
adsl_1 <- adsl_1 %>%
  mutate(MNTFL = case_when(
    ITTEFL == "Y" ~ "Y",
    ITTEFL == "N" ~ "N"))
```
##MNTFLN(48)
```{r}
adsl_1 <- adsl_1 %>%
  mutate(MNTFLN = case_when(
    ITTEFL == "Y" ~ 1,
    ITTEFL == "N" ~ 0))
```
##LTFUEL(49)
```{r}
ds <- as.data.frame(ds)
c_1 <- ds %>% select(c(USUBJID, DSSCAT, EPOCH ,DSDECOD)) 
adsl_1 <- adsl_1 %>% full_join(c_1)

adsl_1 <- adsl_1 %>% 
  mutate(LTFUFL = case_when(
    DSSCAT == "STUDY CONCLUSION" & EPOCH == "FOLLOW-UP" & (DSDECOD == "COMPLETED" | DSDECOD == "CONTINUATION TO FOLLOW UP PHASE")~ "Y" ,
    !(DSSCAT == "STUDY CONCLUSION" & EPOCH == "FOLLOW-UP" & (DSDECOD == "COMPLETED" | DSDECOD == "CONTINUATION TO FOLLOW UP PHASE"))~ "N"))
         
adsl_1 <- distinct(adsl_1,USUBJID,.keep_all = TRUE)
rm(c_1)
```
##LTFUFLN(50)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(LTFUELN = case_when(
    DSSCAT == "STUDY CONCLUSION" & EPOCH == "FOLLOW-UP" & (DSDECOD == "COMPLETED" | DSDECOD == "CONTINUATION TO FOLLOW UP PHASE")~ 1 ,
    TRUE ~ 0)) %>% select( -EPOCH )
```
##SCRNFL(41)
```{r}
ds <- as.data.frame(ds)
temp41 <- ds %>% select(USUBJID,DSSTDTC,VISITNUM,DSSCAT)
adsl_1 <- adsl_1 %>% full_join(temp41)
adsl_1 <- distinct(adsl_1,USUBJID, .keep_all = TRUE)
sv <- as.data.frame(sv)
temp41.1 <- sv %>% select(USUBJID,SVSTDTC)
adsl_1 <- adsl_1 %>% full_join(temp41.1)
adsl_1 <- distinct(adsl_1,USUBJID,.keep_all = TRUE)
adsl_1 <- adsl_1 %>%
  mutate(SCRNFL = case_when(
    ((toupper(DSSCAT )== "SCREEN" & DSSTDTC != "NULL") | (as.integer(VISITNUM)=="10" & SVSTDTC != "NULL" )) ~"Y",
    TRUE ~ "N"))
rm(temp41,temp41.1)
```
##SCRNFN(42)
```{r}
adsl_1 <- adsl_1 %>%
  mutate(SCRNFN = case_when(
    (toupper(DSSCAT )== "SCREEN" & DSSTDTC != "NULL") | (as.integer(VISITNUM)=="10" & SVSTDTC != "NULL" ) ~1,
    TRUE ~ 0)) %>% select(-DSSTDTC,-VISITNUM,-SVSTDTC)
```
##ENRLFL(43)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(ENRLFL = case_when(
    DSDECOD == "INFORMED CONSENT OBTAINED" & DSSCAT == "STUDY" ~"N",
    TRUE ~ "Y"))
```
##ENRLFN(44)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(ENRLFN = case_when(
    DSDECOD == "INFORMED CONSENT OBTAINED" & DSSCAT == "STUDY" ~"0",
    TRUE ~ "1"))
```
##CVFFL(51)
```{r}
lb <- as.data.frame(lb)
temp51 <- lb %>% select(USUBJID,LBTESTCD,LBMETHOD,LBSTRESN)
adsl_1 <- adsl_1 %>% full_join(temp51)
adsl_1 <- distinct(adsl_1,USUBJID, .keep_all = TRUE)

adsl_1 <- adsl_1 %>% 
  mutate(CVFFL = case_when(
    LBTESTCD == "HIV1RNA" & LBMETHOD == "POLYMERASE CHAIN REACTION" & LBSTRESN >= "200" ~ "Y",
    TRUE ~ "N"))
rm(temp51)
```
##CVFFN(52)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(CVFFN = case_when(
    LBTESTCD == "HIV1RNA" & LBMETHOD == "POLYMERASE CHAIN REACTION" & LBSTRESN >= "200" ~ 1,
    TRUE ~ 0)) %>% select(-LBTESTCD,-LBMETHOD,-LBSTRESN)
```
##


##MNTCMPS(63)
```{r}
adsl_1 <- adsl_1 %>% mutate(MNTCMPS = case_when(
  MNTFL == "Y" & DSSCAT == "STUDY CONCLUSION" ~"COMPLETED",
  MNTFL == "Y" & DSSCAT == "STUDY TREATMENT DISCONTINUATION" ~"WITHDRAWN",
  MNTFL == "Y" ~"ONGOING"))
```
##MNTCMPSN(64)
```{r}
adsl_1 <- adsl_1 %>%mutate(MNTCMPSN=case_when(
  MNTCMPS == "ONGOING" ~ 1,
  MNTCMPS == "COMPLETED" ~2,
  MNTCMPS == "WITHDRAWN" ~3))
```
##LTFCMPS(66)
```{r}
ds <-as.data.frame(ds)
d_1 <- ds %>%  select(USUBJID,DSSCAT,EPOCH,DSDECOD) 
adsl_1 <- adsl_1 %>% full_join(d_1)
adsl_1 <- distinct(adsl_1,USUBJID,.keep_all = TRUE)
adsl_1 <- adsl_1 %>% 
  mutate(LTFCMPS=case_when(
    (DSSCAT =="STUDY CONCLUSION" & EPOCH=="FOLLOW-UP" & DSDECOD=="COMPLETED" & TRT01P != "DTG + RPV") ~"COMPLETED",
    (DSDECOD=="CONTINUATION TO FOLLOW UP PHASE" & TRT01P !="DTG + RPV" )~"ONGOING")) %>% 
  select(-DSSCAT,-EPOCH,-DSDECOD)

adsl_1$LTFCMPS[is.na(adsl_1$LTFCMPS)]=""
rm(d_1)
```
##LTFCMPSN(67)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(LTFCMPSN = case_when(
    LTFCMPS == "ONGOING" ~1,
    LTFCMPS == "COMPLETED" ~2,
    LTFCMPS == "WITHDRAWAL" ~ 3))
```
##LSEFL(68)
```{r}
ce <- as.data.frame(ce)
ce_1 <-ce %>% select(c(STUDYID,USUBJID,CECAT))
adsl_1 <- adsl_1 %>% full_join(ce_1)
suppce <- as.data.frame(suppce)
suppce_1 <-suppce %>% select(c(STUDYID, USUBJID,QVAL, QNAM))
adsl_1 <- adsl_1 %>% full_join(suppce_1)
adsl_1 <- distinct(adsl_1,USUBJID,.keep_all = TRUE)  
adsl_1 <- adsl_1 %>% 
  mutate(LSEFL = case_when(
    (CECAT=="LIVER EVENT REPORTING" & suppce$QNAM=="LERMX" & suppce$QVAL=="LIVER EVENT STOPPING CRITERIA") ~"Y",
    !(CECAT=="LIVER EVENT REPORTING" & suppce$QNAM=="LERMX" & suppce$QVAL=="LIVER EVENT STOPPING CRITERIA") ~"N")) %>% 
  select(-CECAT,-QVAL,-QNAM)
rm(ce_1,suppce_1 )
```
##LSEFN(69)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(LSEFLN = case_when(
    LSEFL == "Y" ~ 1,
    TRUE ~0))
```
##DTHFN(71)
```{r}
adsl_1 <- adsl_1 %>% 
   mutate(DTHFN = case_when(
    DTHFL == "Y" ~ "1",
    TRUE ~ ""))
```
##ACOUNTRY(72)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(ACOUNTRY = case_when(
    COUNTRY == "CAN" ~"CANADA",
    COUNTRY == "USA" ~"UNITED STATES"))
temp73 <- ds %>%  filter(VISIT=="END OF MAINTENANCE PHASE" | 
                           DSSCAT=="STUDY TREATMENT DISCONTINUATION") %>% 
  select(USUBJID,VISIT,DSSCAT)
```
##TRTSDT(61)
 
```{r}
temp61 <- ex %>% 
  filter(EXTRT == "CAB LA"| EXTRT == " RPV LA" | EXTRT =="DOLUTEGRAVIR/RILPIVIRINE") %>% 
  group_by(USUBJID) %>% 
  mutate(TRTSDT = as.Date(min(EXSTDTC))) %>% 
  summarise_all(first) %>% 
  select(USUBJID,TRTSDT)
adsl_1 <-adsl_1 %>% full_join(temp61)
rm(temp61)
```



##TRTEDT(62)DERIVED
```{r}
temp62 <- ex %>% 
  filter(EXTRT == "CAB LA"| EXTRT == " RPV LA" | EXTRT =="DOLUTEGRAVIR/RILPIVIRINE") %>% 
  group_by(USUBJID) %>% 
  mutate(TRTEDT = as.Date(max(EXSTDTC,EXENDTC))) %>% 
  summarise_all(last) %>% 
  select(USUBJID,TRTEDT)
adsl_1 <-adsl_1 %>% full_join(temp62)
rm(temp62)
```
#MDSFL(73)
```{r}
temp73 <- ds %>%  filter(VISIT=="END OF MAINTENANCE PHASE" |
                           DSSCAT=="STUDY TREATMENT DISCONTINUATION") %>% 
  select(USUBJID,VISIT,DSSCAT)
temp73.1 <- adsl_1 %>% 
  full_join(temp73) %>% 
  mutate(MDSFL= case_when(
    VISIT=="END OF MAINTENANCE PHASE" | 
      (DSSCAT=="STUDY TREATMENT DISCONTINUATION" &
      !is.na(TRTEDT)) ~ "Y",
    TRUE ~ "N")) %>% 
  select(USUBJID,MDSFL)
adsl_1 <- adsl_1 %>% full_join(temp73.1)
rm(temp73,temp73.1)
```
##DISCREAS(74)
```{r}
rm1 <- ds %>% 
  filter(VISIT=="END OF MAINTENANCE PHASE" | 
           DSSCAT=="STUDY TREATMENT DISCONTINUATION") 
rm2 <- adsl_1%>% 
  full_join(rm1) %>% 
  mutate(DISCREAS=case_when(
    MDSFL == "Y" &
      VISIT=="END OF MAINTENANCE PHASE" | 
      DSSCAT=="STUDY TREATMENT DISCONTINUATION" ~ as.character(DSDECOD),
    TRUE ~ " ")) %>% select(USUBJID,DISCREAS)
adsl_1 <- adsl_1 %>% full_join(rm2)
rm(rm1,rm2)
```
##MNTSDT(75)
```{r}

adsl_1 <- adsl_1 %>%  mutate(MNTSDT = TRTSDT)
```
##BMIBL(80)
```{r}
tempp <- vs %>% 
  select(USUBJID,VSDY,VSORRES,VSTEST ) %>% 
  filter(VSDY <= 1) %>% 
  filter(VSTEST == "Height" |VSTEST == "Weight") %>% 
  pivot_wider(names_from = VSTEST, values_from = VSORRES )
tempp$Height <- as.numeric(tempp$Height)
tempp$Weight <- as.numeric(tempp$Weight)
tempp <- tempp %>% mutate(Height = tempp$Height/100) %>% 
  mutate(BMIBL = tempp$Weight / Height^2) %>% select(-VSDY)
adsl_1 <- adsl_1 %>% full_join(tempp)
adsl_1 <- distinct(adsl_1,USUBJID,.keep_all = TRUE) 
rm(tempp)
```
##BMIGR1(81)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(BMIGR1 = case_when(
    BMIBL < 30 ~ "<30",
    BMIBL >= 30 ~ ">=30" ))
```
##BMIGR1N(82)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(BMIGR1N = case_when(
    BMIBL < 30 ~ "1",
    BMIBL >= 30 ~ "2",
    TRUE ~ ""))
```
##BMIUNIT(83)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(BMIUNIT= case_when(
    !is.na(BMIBL) ~"kg/m2",
    TRUE~"")) %>% select(-Height,-Weight)
```
##HTUNIT(84)
```{r}
temp84 <- vs %>% 
  filter(VSTESTCD == "HEIGHT") %>%select(USUBJID,VSSTRESN,VSSTRESU,VSTESTCD)
rm10<- adsl_1 %>% full_join(temp84)
rm10 <- distinct(rm10,USUBJID,.keep_all = TRUE)
rm10<- rm10 %>%  mutate(HTUNIT = case_when(
  VSTESTCD == "HEIGHT" & !is.na(VSSTRESN) ~ as.character(VSSTRESU),
  TRUE ~ " ")) %>% select(USUBJID,HTUNIT)
adsl_1 <- adsl_1 %>% full_join(rm10)
rm(rm10,temp84)
```
##HEIGHTBL(85)
```{r}

temp85 <- vs %>% 
  group_by(USUBJID) %>% filter(VSDTC == min(as.Date(VSDTC))) %>% 
  ungroup() %>% 
  pivot_wider(.,names_from = VSTESTCD ,values_from = VSORRES) %>% 
  select(USUBJID,HEIGHT,VSDTC) %>% 
  group_by(USUBJID) %>% 
  mutate(HEIGHT = unique(HEIGHT[!is.na(HEIGHT)])) %>% 
  distinct() %>% 
  ungroup()
temp85.1 <- adsl_1 %>% select(USUBJID) %>% full_join(temp85) %>% 
  mutate(HEIGHTBL=HEIGHT) %>% 
  select(USUBJID,HEIGHTBL)
adsl_1 <- adsl_1 %>%  full_join(temp85.1)
rm(temp85,temp85.1)
```
##WTUNIT(86)
```{r}
temp86 <- vs %>% 
  filter(VSTESTCD == "WEIGHT") %>%select(USUBJID,VSSTRESN,VSSTRESU,VSTESTCD)
rm10<- adsl_1 %>% full_join(temp86)
rm10 <- distinct(rm10,USUBJID,.keep_all = TRUE)
rm10<- rm10 %>%  mutate(WTUNIT = case_when(
  VSTESTCD == "WEIGHT" & !is.na(VSSTRESN) ~ as.character(VSSTRESU),
  TRUE ~ " ")) %>% select(USUBJID,WTUNIT)
adsl_1 <- adsl_1 %>% full_join(rm10)
rm(rm10,temp86)
```

##WEIGHTBL(87)
```{r}
temp87 <- vs %>% 
  group_by(USUBJID) %>% filter(VSDTC == min(as.Date(VSDTC))) %>% 
  ungroup() %>% 
  pivot_wider(.,names_from = VSTESTCD ,values_from = VSORRES) %>% 
  select(USUBJID,WEIGHT,VSDTC) %>% 
  group_by(USUBJID) %>% 
  mutate(WEIGHT = unique(WEIGHT[!is.na(WEIGHT)])) %>% 
  distinct() %>% 
  ungroup()
temp87.1 <- adsl_1 %>% select(USUBJID) %>% full_join(temp87) %>% 
  mutate(WEIGHTBL=WEIGHT) %>% 
  select(USUBJID,WEIGHTBL)
adsl_1 <- adsl_1 %>%  full_join(temp87.1)
rm(temp87,temp87.1)
```
##condn 1:If subject has a pre-treatment record where CO.COVAL="HBV DNA DETECTED" then HEPBST="Positive". 
```{r}
coval<- co %>% filter(COVAL=="HBV DNA DETECTED") %>% distinct(USUBJID)
```
##condn 2:Else if subject has a pre-treatment record where LB.LBTESTCD in ("HBVDNA" "HBVDNAC" "HBVDNAL"): if LB.LBSTRESN ne . or LB.LBORRES ne "<x" then HEPBST="Positive", else HEPBST="Negative".
```{r}
lbtestcd <- lb %>% filter(LBTESTCD=="HBVDNA"|LBTESTCD=="HBVDNAC"|LBTESTCD=="HBVDNAL") %>% distinct(USUBJID)
```

##condn 3:Else if subject has a pre-treatment record where LB.LBTESTCD="HBSAGZ":  if LB.LBSTRESC="REACTIVE" then HEPBST="Positive", else if LB.LBSTRESC="NON-REACTIVE" then HEPBST="Negative".
```{r}
lb1<- lb %>% filter(LBTESTCD=="HBSAGZ") %>% filter(LBSTRESC=="NON-REACTIVE")%>% distinct(USUBJID)
for (i in seq(nrow(lb1))){
  id <- which(adsl_1$USUBJID ==as.character(lb1[i,"USUBJID"]))
  adsl_1[id,"HEPBST"] = "Negative"
}
lb2<- lb %>% filter(LBTESTCD=="HBSAGZ") %>% filter(LBSTRESC=="REACTIVE")%>% distinct(USUBJID)
for (i in seq(nrow(lb2))){
  id <- which(adsl_1$USUBJID ==as.character(lb2[i,"USUBJID"]))
  adsl_1[id,"HEPBST"] = "Positive"
}
  
for (i in seq(nrow(adsl_1))){
  if (is.na(adsl_1[i,"HEPBST"] == "NA")){
    adsl_1[i,"HEPBST"] = " "
  }
}
rm(lb1,lb2)
```
##HEPBSTCD(89)
```{r}
adsl_1 <- adsl_1 %>%
  mutate(HEPBSTCD=case_when(
    HEPBST == "Negative" ~0,
    HEPBST == "Positive"~ 1,))
```
####...................HEPCST(90)

##condn 1:If subject has a pre-treatment record where LB.LBTESTCD in ("HCVRNA" "HCVRNAL"):
```{r}
lb_1 <- lb %>% filter(LBTESTCD == "HCVRNA" | LBSTRESN == "HCVRNAL") %>%  distinct(USUBJID)
for (i in seq(nrow(lb_1))){
  id <- which(adsl_1$USUBJID ==as.character(lb_1[i,"USUBJID"]))
  adsl_1[id,"HEPCST"] = "Negative"
}
lb_1.1 <- lb %>% filter(LBTESTCD == "HCVRNA" | LBSTRESN == "HCVRNAL") %>% filter(LBORRES != "TARGET NOT DETECTED" | is.na(LBSTRESN)== F )%>%  distinct(USUBJID)
for (i in seq(nrow(lb_1.1))){
  id <- which(adsl_1$USUBJID ==as.character(lb_1.1[i,"USUBJID"]))
  adsl_1[id,"HEPCST"] = "Positive"
}
```
##condn 2:Else if subject has a pre-treatment record where LB.LBTESTCD="HCVABZ":
```{r}
lb_2 <- lb %>%  filter(LBTESTCD=="HCVABZ") %>%  filter(LBSTRESC=="REACTIVE" | LBSTRESC=='BORDERLINE') %>% distinct(USUBJID)
for (i in seq(nrow(lb_2))){
  id <- which(adsl_1$USUBJID ==as.character(lb_2[i,"USUBJID"]))
  adsl_1[id,"HEPCST"] = "Positive"
}
lb_2.1 <- lb %>%  filter(LBTESTCD=="HCVABZ") %>% filter(LBSTRESC=="NON-REACTIVE") %>%  distinct(USUBJID)
for (i in seq(nrow(lb_2.1))){
  id <- which(adsl_1$USUBJID ==as.character(lb_2.1[i,"USUBJID"]))
  adsl_1[id,"HEPCST"] = "Negative"
}
for (i in seq(nrow(adsl_1))){
  if (is.na(adsl_1[i,"HEPCST"] == F )){
    adsl_1[i,"HEPCST"] = ""
  }
}
rm(lb_1,lb_1.1)
rm(lb_2,lb_2.1)
```
##HEPCSTCD(91)
```{r}
adsl_1 <- adsl_1 %>% mutate(HEPCSTCD=case_when(
  HEPCST == "Negative" ~ 0,
  HEPCST == "Positive" ~ 1))
```
##.................HEPBCST(92)
```{r}
adsl_1<- adsl_1 %>% mutate(HEPBCST=case_when(
  HEPBSTCD == 1 & HEPCSTCD == 0 ~ "B only",
  HEPBSTCD == 0 & HEPCSTCD == 1 ~ "C only",
  HEPBSTCD == 1 & HEPCSTCD == 1 ~ "B and C",
  HEPBSTCD == 0 & HEPCSTCD == 0 ~ "Neither"))
```
##.HEPBCSCD(93)
```{r}
adsl_1 <- adsl_1 %>% mutate(HEPBCSCD= case_when(
  HEPBCST == "B only" ~ 1,
  HEPBCST == "C only" ~ 2,
  HEPBCST == "B and C" ~ 3,
  HEPBCST == "Neither" ~ 4))

```
##MTH12SDT(97)
##VALUE OF SVSTDTC WHERE VISIT='MONTH 12
```{r}
SVSTDTC <- as.Date(sv$SVSTDTC)
sv1 <- sv %>% filter(VISIT=="MONTH 12") %>% select(USUBJID, MTH12SDT = SVSTDTC) 
adsl_1 <- adsl_1 %>%  full_join(sv1) %>% mutate(MTH12SDT = as.Date(MTH12SDT))
rm(sv1)
```
##MTH26SDT(98)
```{r}
sv2 <- sv %>% filter(VISIT=="MONTH 26") %>%  select(USUBJID,MTH26SDT = SVSTDTC) 
adsl_1 <- adsl_1 %>%  full_join(sv2)%>% mutate(MTH26SDT = as.Date(MTH26SDT))
rm(sv2)
```
##HIVRKFL(99)
```{r}
Y8.1 <- y8%>% filter(Y8TESTCD=="HIVRFKNW") 
rm1 <- adsl_1 %>% full_join(Y8.1)
rm1 <- rm1 %>% mutate( HIVRKFL = case_when(
    Y8TESTCD =="HIVRFKNW" ~ "Y",
    TRUE ~ "N")) %>% select(USUBJID,HIVRKFL)
adsl_1<- adsl_1 %>% full_join(rm1)
rm(Y8.1,rm1)
```

##HIVRK(100)
```{r}
mh <- as.data.frame(mh)
temp106 <- mh %>% filter(MHTERM=="DEPRESSION" &
                           MHOCCUR=="Y" & 
                           VISITNUM==10 & 
                           MHSTRF=="BEFORE")
rm12<- temp106%>% full_join(temp106)
rm12<- rm12 %>% 
  mutate(HISDEPFL= case_when(
    MHTERM=="DEPRESSION" & 
      MHOCCUR=="Y" &
      VISITNUM==10 & 
      MHSTRF=="BEFORE" ~"Y",
    TRUE ~"N")) %>% select(USUBJID,HISDEPFL)
adsl_1 <- adsl_1 %>% full_join(rm12)
adsl_1$HISDEPFL[is.na(adsl_1$HISDEPFL)]= "N"
rm(temp106,rm12)
```
##HISSUIFL(107)
```{r}
rm1 <- mh %>% 
  filter(MHTERM == "SUICIDAL IDEATION" &
           MHOCCUR == "Y" &
           VISITNUM == 10 &
           MHSTRF == "BEFORE")
rm1 <- rm1 %>% 
  mutate(HISSUIFL= case_when(
    MHTERM == "SUICIDAL IDEATION" &
      MHOCCUR == "Y" & 
      VISITNUM == 10 & 
      MHSTRF == "BEFORE" ~"Y",
    TRUE ~ "N")) %>% select(USUBJID,HISSUIFL)
adsl_1 <- adsl_1 %>% full_join(rm1)
adsl_1$HISSUIFL[is.na(adsl_1$HISSUIFL)] = "N"
rm(rm1)
```
## HISANXFL(108)
```{r}
rm1 <- mh %>% 
  filter(MHTERM == "ANXIETY" &
           MHOCCUR == "Y" &
           VISITNUM == 10 &
           MHSTRF == "BEFORE")
rm1<- rm1 %>% 
  mutate(HISANXFL= case_when(
    MHTERM== "ANXIETY" &
      MHOCCUR=="Y" & 
      VISITNUM==10 & 
      MHSTRF=="BEFORE" ~"Y",
    TRUE ~"N")) %>% select(USUBJID,HISANXFL)
adsl_1 <- adsl_1 %>% full_join(rm1)
adsl_1$HISANXFL[is.na(adsl_1$HISANXFL)] = "N"
rm(rm1)
```
##HISANX (109)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(HISANX= case_when(
    HISANXFL == "Y" ~"previous history of anxiety",
    TRUE ~ "no previous history of anxiety"))
```
##HISSUI(110)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(HISSUI = case_when(
    HISSUIFL == "Y" ~"previous history of suicidal ideation",
    TRUE ~"no previous history of suicidal ideation"))
```
##HISDEP(111)
```{r}
adsl_1 <- adsl_1 %>% 
  mutate(HISDEP= case_when(
    HISDEPFL=="Y" ~"previous history of depression" ,
    TRUE ~"no previous history of depression")) 
```
##CD4BL(101)

```{r}
LBDTC <- as.Date(lb$LBDTC)
rm1 <- lb %>% 
  filter(LBTESTCD=="CD4") %>% 
  group_by(USUBJID)
rm1 <- adsl_1 %>%  full_join(rm1)
rm1 <- rm1 %>% mutate(CD4BL = case_when(
  LBTESTCD == "CD4" &
    LBDTC <= TRTSDT ~ LBSTRESN)) %>% 
  select(USUBJID,CD4BL) %>% 
  distinct(USUBJID,.keep_all = TRUE)
adsl_1 <- adsl_1 %>%  full_join(rm1)
rm(rm1)
```
##CD4BLGR1(102)
```{r}
adsl_1 <- adsl_1 %>% mutate(CD4BLGR1= case_when(
  CD4BL < 350 ~ "<350",
  CD4BL =350 & CD4BL <500 ~ "350-<500",
  CD4BL >= 500 ~ ">=500",
  TRUE ~ ""))

```
##CD4BLGR1N(103)
```{r}
adsl_1 <- adsl_1 %>% mutate(CD4BLGR1N=case_when(
  CD4BL < 350 ~ 1,
  CD4BL =350 & CD4BL <500 ~ 2,
  CD4BL >= 500 ~ 3)) 
```
If subject has a record where CE.CECAT="HIV ASSOCIATED CONDITIONS" and CE.CESTDTC non-missing and CE.CESTDTC is on/before TRTSDT then CDCBCATN=3. Else if . < CD4BL < 200 then CDCBCATN=3, else if 200 =< CD4BL < 500 then CDCBCATN=2, else if CD4BL >= 500 then CDCBCATN=1. Else if CD4BL is missing then find the subjects latest record where LB.LBTESTCD="CD4LY" and LB.LBDTC is on/before TRTSDT, and if . < LB.LBSTRESN < 14 then CDCBCATN =3, else if 14 =< LB.LBSTRESN < 26 then CDCBCATN =2, else if LB.LBSTRESN >= 26 then CDCBCATN=1. Otherwise CDCBCATN is missing. Where CD4BL is the latest value of LB.LBSTRESN where LB.LBTESTCD="CD4" and numeric date part of LB.LBDTC is on or before TRTSDT.
```{r}
CESTDTC <- as.Date(ce$CESTDTC)
rm1 <- ce %>% filter(CECAT=="HIV ASSOCIATED CONDITIONS")
rm1 <- adsl_1 %>% full_join(rm1)
rm1 <- rm1 %>% mutate(CDCBCATN=case_when(
  CECAT=="HIV ASSOCIATED CONDITIONS" &
    !is.na(CESTDTC) &
    CESTDTC <= TRTSDT ~ 3,
  CD4BL < 200 ~ 3,
  CD4BL >= 200 & CD4BL < 500 ~2,
  CD4BL >=500 ~ 1)) %>% select(USUBJID,CDCBCATN) 
adsl_1<-adsl_1 %>% full_join(rm1)
rm(rm1)

```
##CDCBLCAT(105)
```{r}
adsl_1 <- adsl_1 %>% mutate(CDCBLCAT=case_when(
  CDCBCATN == 1 ~ "Stage I",
  CDCBCATN == 2 ~ "Stage II",
  CDCBCATN == 3 ~ "Stage III",
  TRUE ~ ""))
```

```{r}
saveRDS(adsl_1,"adsl_1.rds")
```
```{r}
write_sas(adsl_1,"adsl_1.sas7bdat")
```


