---
title: "Untitled"
author: "Smriti karki"
date: "10/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#loading library
```{r}
library(haven)
library(dplyr)
library(tidyverse)
library(lubridate)
library(stringr)
```

```{r}
demo <- read_sas("E:/Numeric mind/adam/rawdata/demo.sas7bdat",NULL)
dm <- read_sas("E:/Numeric mind/adam/rawdata/dm.sas7bdat",NULL)
investig <- read_sas("E:/Numeric mind/adam/rawdata/investig.sas7bdat",NULL)
race <- read_sas("E:/Numeric mind/adam/rawdata/race.sas7bdat",NULL)
dth <- read_sas("E:/Numeric mind/adam/rawdata/dth.sas7bdat",NULL)
prvtrial <- read_sas("E:/Numeric mind/adam/rawdata/prvtrial.sas7bdat",NULL)

exposure <- read_sas("E:/Numeric mind/adam/rawdata/exposure.sas7bdat",NULL)
```
```{r}
dm1 <- demo %>%  left_join(investig)

dm1 <- dm1 %>% left_join(prvtrial)
dm1 <- dm1 %>% left_join(dth)
dm1 <- dm1 %>% left_join(race)
# exposure$SUBJID <- as.character(exposure$SUBJID)
# dm1 <- dm1 %>% left_join(exposure)
```

#ASE WHEN PRVTRIAL.PTSTUDY IS NOT NULL AND PRVTRIAL.PTSUBJID IS NOT NULL THEN PRVTRIAL.PTSTUDY||'.'|| LPAD(PRVTRIAL.PTSUBJID,6,0) 
ELSE TRIM(UPPER(DEMO.STUDYID))||'.'||LPAD(DEMO.SUBJID,6,'0')  END
#SUBJID,SITEID
```{r}
dm1$PTSUBJID <-str_pad(dm1$PTSUBJID,6, pad = "0")
dm1$USUBJID <- trimws(paste(dm1$PTSTUDY,".",dm1$PTSUBJID),which = c("both"))

dm1 <- dm1[-c(9),]
dm1$STUDYID<- trimws(dm1$STUDYID, which = c("both"))
dm1$STUDYID <- toupper(dm1$STUDYID)
dm1$SUBJID<-replace(dm1$SUBJID, dm1$SUBJID==29,"MULTIPLE")
```
#SITEID
```{r}
dm1 <- dm1 %>% rename(SITEID = CENTREID)

dm1$COUNTRY <- toupper(dm1$COUNTRY)
dm1$COUNTRY <- replace(dm1$COUNTRY,dm1$COUNTRY == "UNITED STATES", "USA") 
dm1$COUNTRY <- replace(dm1$COUNTRY,dm1$COUNTRY == "CANADA", "CAN")
dm1$INVID <- replace(dm1$INVID, is.na(dm1$INVID)== T,dm1$INVID)
dm1$INVNAME <- replace(dm1$INVNAME, is.na(dm1$INVNAME)== T,dm1$INVNAME)
dm1 <- dm1 %>% rename(INVNAM= INVNAME) 
dm1$INVNAM <- toupper(dm1$INVNAM)
```


TRIM(UPPER(INVESTIG.INVNAME))
```{r}
# race$SUBJID <- as.character(race$SUBJID)

dm1 <- dm1 %>% 
  mutate(RACE = case_when(
    RACECCD == 13| RACECCD == 14 |RACECCD == 15 |RACECCD == 16 ~ "ASIAN",
    RACECCD == 18 | RACECCD == 19 ~ "WHITE",
    TRUE ~ "MULTIPLE")) 
```

```{r}

dm1 <- dm1 %>% rename(DTHDTC = DDDT)%>%
  mutate(DTHFL = "")

# 
# demo1$DTHDTC[is.na(demo1$DTHDTC)]<- na.omit(demo1$DTHDTC)
```
#ETHNIC
```{r}
dm1 <- dm1 %>% mutate(ETHNIC = case_when(
  ETHNICCD == 1 ~ "HISPANIC OR LATINO",
  ETHNICCD == 2 ~ "NOT HISPANIC OR LATINO"))
```
CASE
WHEN LENGTH(REPLACE(TRIM(DEMO.DOBD_),'-')) = 9 THEN TO_CHAR(TO_DATE(DEMO.DOBD_,'DDMONYYYY'),'YYYY-MM-DD')
WHEN LENGTH(REPLACE(TRIM(DEMO.DOBD_),'-')) = 7 THEN TO_CHAR(TO_DATE(REPLACE(TRIM(DEMO.DOBD_),'-'),'MONYYYY'),'YYYY-MM')
WHEN LENGTH(REPLACE(TRIM(DEMO.DOBD_),'-')) = 6 THEN TO_CHAR(TO_DATE(REPLACE(TRIM(DEMO.DOBD_),'-'),'DDYYYY'),'YYYY---DD')
WHEN LENGTH(REPLACE(TRIM(DEMO.DOBD_),'-')) = 5 THEN TO_CHAR(TO_DATE(REPLACE(TRIM(DEMO.DOBD_),'-'),'DDMON'),'--MM-DD')
when length(replace(TRIM(DEMO.DOBD_),'-')) = 4 then TRIM(replace(TRIM(DEMO.DOBD_),'-'))
END
#SEX
```{r}
# dm1 <- dm1 %>% rename(SEX = GENDERCD)
dm1 <- dm1 %>% mutate(BRTHDTC=sub(".*-","", DOBD_))
dm1$BIRTHDTC <- as.character(dm1$BIRTHDT)

```
left join(SELECT SUBJID SUBJID6, MIN(CASE WHEN EXSTDT IS NOT NULL THEN 
NVL2(EXSTDT,TO_CHAR(EXSTDT,'YYYY-MM-DD'),'-----')||RPAD('T',1+MOD(8-LENGTH(TRIM(EXSTTM)),3),'0')||TRIM(EXSTTM)END)AS RFSTDTC,

```{r}
library(lubridate)
temp <-  exposure%>% separate(EXSTTM,c("a","b","c")) %>% unite("EXSTTM",a:b)
temp$EXSTDT <- as.character(temp$EXSTDT)

#   
# 
temp$EXSTTM<- gsub("_",":",temp$EXSTTM)
temp$EXSTTM <- as.character(temp$EXSTTM)

temp <- temp %>% unite("aa",c(EXSTDT,EXSTTM),sep = "T") %>% select(SUBJID,aa) 

temp <- temp  %>% group_by(SUBJID) %>%
  mutate(RFSTDTC= min(aa)) %>% ungroup()
temp <- temp %>% select(SUBJID,RFSTDTC) %>% distinct()
temp$SUBJID<- as.character(temp$SUBJID)
dm1 <- dm1 %>% left_join(temp)
dm1$RFSTDTC[is.na(dm1$RFSTDTC)]<- ""
dm1 <- dm1 %>% mutate(RFXSTDTC = RFSTDTC)
```
#MAX(CASE WHEN EXSTDT IS NOT NULL THEN NVL2(EXSTDT,TO_CHAR(EXSTDT,'YYYY-MM-DD'),'-----')||RPAD('T',1+MOD(8-LENGTH(TRIM(EXSTTM)),3),'0')||TRIM(EXSTTM)
END)AS MAXSTDTC,
```{r}
temp <-  exposure%>% separate(EXSTTM,c("a","b","c")) %>% unite("EXSTTM",a:b)
temp$EXSTDT <- as.character(temp$EXSTDT)
temp$EXSTTM<- gsub("_",":",temp$EXSTTM)
temp$EXSTTM <- as.character(temp$EXSTTM)

temp <- temp %>% unite("aa",c(EXSTDT,EXSTTM),sep = "T") %>% select(SUBJID,aa) 

temp <- temp  %>% group_by(SUBJID) %>%
  mutate(MAXSTDTC= max(aa)) %>% ungroup()
temp <- temp %>% select(SUBJID,MAXSTDTC) %>% distinct()
temp$SUBJID<- as.character(temp$SUBJID)
dm1 <- dm1 %>% left_join(temp)
dm1$MAXSTDTC[is.na(dm1$MAXSTDTC)]<- ""

```
```{r}
dm1 <- dm1 %>% mutate(DOMAIN = "DM")
dm1 <- dm1 %>% mutate(RFICDTC = as.character(CNSDT))
dm1 <- dm1 %>% select(-c(VISITNUM,VISIT,ETHNICCD,DOBD_,GENDERCD,ETSBJSTS,PTYN,PTSTUDY,PTCENTRE,PTSUBJID,SEQ,RACECCD,CNSDT))
dm1 <- dm1 %>% select(STUDYID,DOMAIN,USUBJID,SUBJID,RFSTDTC,RFXSTDTC,RFICDTC,DTHDTC,DTHFL,SITEID,INVID,INVNAM,BRTHDTC,SEX,RACE,ETHNIC,MAXSTDTC,COUNTRY)

```


#MAX(CASE WHEN EXENDT IS NOT NULL THEN TO_CHAR(EXENDT,'YYYY-MM-DD')END)AS RFXENDTC



