---
title: "jobs_gender"
author: "Smriti karki"
date: "6/15/2020"
output: 
  html_document:
    keep_md: yes
    df: paged
    theme: readable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = FALSE,
	warning = FALSE)
```

## Load library
```{r}
library(dplyr)
library(ggplot2)
library(readr)
library(tidyverse)

```



##Loading data
```{r}
jobs_gender <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-03-05/jobs_gender.csv")
jobs_gender


```

##To add column i.e male female worker proportion
```{r}
prop_male_female <- jobs_gender %>% 
  select(year,occupation,total_workers,workers_male,workers_female) %>% 
  mutate(prop = workers_male/workers_female)
prop_male_female
```

##To filter the minor_category:architecture and engineering
```{r}
arch_eng <- jobs_gender %>% select(year,occupation,minor_category,major_category,workers_male,workers_female) %>% 
  filter(minor_category=="Architecture and Engineering")
arch_eng

```
##To arrange total earnings in ascending orders according to wages
```{r}
asc_wage <- jobs_gender %>% 
   select(year,occupation,major_category,minor_category,total_earnings) %>% 
   arrange(total_earnings)
 asc_wage
 
```
##To find mean wage of whole major category
```{r}
mean_wage <- jobs_gender %>% 
   group_by(major_category) %>% 
   summarise(ave_wage = mean(total_earnings))
 mean_wage
 
```
##To find number of male median earning > 50000 and female median earning >30000
```{r}
number <- jobs_gender %>% 
   filter((total_earnings_male<50000) & (total_earnings_female <30000) ) %>% 
   group_by(occupation) %>% 
   summarise(total = n())
number
```

##To find average earning of all jobs
```{r}
average <- jobs_gender %>% 
  summarise(average=mean(total_earnings))
   
average
```
##Female earning more than average earning
```{r}
high_income <- jobs_gender %>% 
  select(year,occupation,total_earnings_female) %>% 
  filter(total_earnings_female > 49762.09) %>% 
  group_by(occupation) 

high_income
```
##ggplot
```{r}

ggplot(jobs_gender,aes(x=occupation, y= total_workers, fill=occupation))+
           geom_col()+
           guides(fill=F)
```






